\LARGE \bf Autonomous Object Manipulation using a Soft Planar Grasping Manipulator

### 2015-10-11 SoRo reviewer comments/Reviewer Comments Reply 15-10-10.tex

\end{enumerate}

\subsection{Grammar Comments}
\textit{Overall the paper is well-written, but there are some places with awkward or incorrect grammar. 
Examples include 
1)pg 2 line 37 "soft robots do neither require force sensing nor accurate ..."; 
2)pg 3 line 23 "Those seams are prone to rupture ..." refers to the laminated seams, but that isn't clear from phrasing; 
3)pg 7 line 21 "newly registers every single time the position of the placed object." is confusing.}

Thank you for pointing out these grammar mistakes. We proof read the paper and fixed them.

\subsection{Video Attachement}
\textit{The paper should definitely include a video of operation of the arm. The overlaid figures are very well done, but video would be a valuable contribution to understanding the performance of the system, especially since we have no other time dependent graphs of end effector or joint position.}
%
Thank you for this suggestion, the video will be attached again to the revised version of the paper.
%
\subsection{Table 1 Formatting}
\textit{Table 1 needs to be formatted to stay in column}
%
We adjusted the formatting accordingly.
%
\subsection{Variable Definitions}
\textit{I feel like many variables could be more clearly defined. Things such as $L_{meas}$, $\phi$, $g_{off}$ (described in algorithm, but still not clear where measured from),}
%
Thank you for pointing all this out. We added clearer descriptions to the text and more indications in figure 5 and figure 6 to clarify these variables.
%
\textit{$w_{off}$, $L_N$, $\kappa$ (in algorithm 1, not clear if current $\kappa$ or desired or ...),}
%
We added: The end effector offset $\mathbf{w}_{\textrm{off}}$ describes the distance from the root of the gripper, to an offset point close to the lower end of the gripper's palm. It is visualized in the top left corner of Fig. 5.
We also added to the manuscript: The arc length input to the arm's forward kinematics is the $N$-th element of the segment lengths $\mathbf{L}_{\textrm{meas}}$.
%
We assume that it is clear 
$\kappa$ is the variable being optimized for in $\underset{\phi, \, \boldsymbol{\kappa}}{\text{min}}$
%
\textit{$\kappa_{off}$ (defined in algorithm, but not clear again what it was). Some of these terms are on the diagram in Figure 6, but their definition was still not clear to me. This was especially the case since I'm not sure what the multiple green circles on each concentric circle signified. Some terms were also used but not clearly such as "minimal tip transit distance".}
%
$\kappa_{off}$  is now better defined by: "measured manipulator configuration at start". We also clarified the meaning of the \emph{green} circles in the text.
%

%
\subsection{Value for $\delta d$}
\textit{Other items were clearly defined, but it wasn't clear how their value was set such as $\delta d$.}

@@

We revised the text to describe how value for delta d was set

\subsection{Object Settling}
\textit{In Section 4.2, what does it mean for an "object to settle?"}
We consider the object to have settled if it has not moved for 2\unit{s}. We added this sentence to the manuscript.

### 2015-10-11 processing_control.tex
first round of changes to the manuscript
fixed variable problems

\subsection{Existing Procedures}
The forward kinematics algorithm \texttt{forwKin()}, which we employ in this work, assumes piece-wise constant curvature according to \cite{webster2010design}. 
This algorithm was experimentally validated for the soft planar arm in \cite{marchese2014design}.
In order to uniquely fit a configuration representation to measured endpoint data in real-time, we use a previously developed single segment inverse kinematics algorithm \cite{marchese2014design} and refer to it in this work as \texttt{singSegInvKin()}.
The inputs to this block are the start and endpoint measurements in $\mathbb{R}^2$: $\mathbf{E}_n \; \forall n  = 1..N$, where $N$ is the number of segments composing the arm.
The outputs from this block are the representations of the measured manipulator configuration: $\boldsymbol{\kappa}_{\textrm{meas}}$ and $\mathbf{L}_{\textrm{meas}}$.
This work expands on the previously developed cascaded closed-loop curvature controller, whose input is target curvatures $\boldsymbol{\kappa}_{\textrm{target}}$ and whose output is the controlled adjustment of a fluidic drive cylinder array to resolve the error between $\boldsymbol{\kappa}_{\textrm{target}}$ and $\boldsymbol{\kappa}_{\textrm{meas}}$.
In this work we refer to it as the \texttt{curvatureController()}.

@@

\subsection{Autonomous Grasp-and-Place System}
\label{subsec:grasp-place-planner}
The robotic manipulation system is capable of autonomously performing grasp-and-place operations. 
A state flow diagram describing its sensing, planning and executions states is given in Fig. \ref{fig:grasp-and-place-planner}. 
A motion tracker constantly captures the position of the object and passes it along to a routine, which checks for the object to settle. 
After it has settled, the Grasp Object Planner receives the coordinates and radius of the settled object and together with the current curvature values of the arm and gripper, it solves a series of constrained nonlinear optimization problems to generate end-effector poses approaching the object.
Those end-effector poses are essentially waypoints for an optimized path the robot arm should take to get to the final position without the risk of pushing away the object before the gripper arrives there. 
Forcing the arm controller to follow those intermediate waypoints ensures that the arm moves to the object while its null space maintains a convex shape, bending away from the object. 
Furthermore, it allows the arm to move in smaller portions, decreasing the risk of large overshoots due to slip-stick friction between the roller supports and the ground.
This planner is described in more detail in Section~\ref{subsec:grasp_planner}.

@@

\subsection{Grasp Object Planner}
\label{subsec:grasp_planner}
A fundamental component of the grasp-and-place system is its ability to plan a feasible approach motion to the object.
That is, given the location $\left(x_o, \, y_o\right)$ and radius $r_o$ of a round object as well as the manipulator's current configuration $\boldsymbol{\kappa}_{\textrm{meas}}$, we determine a series of locally optimal manipulator configurations $\boldsymbol{\kappa}_i^* \; \forall i \, = 1.. numMoves$ that will, if sequentially achieved, bring the manipulator gradually closer to the object while any part of the arm is not touching the object.
We refer to these as approach configurations.
The process for determining these approach configurations is detailed in the \texttt{planGrasp()} procedure within the Grasp Object Planner, see Algorithm \ref{alg:planGrasp}.
The planner is visualized in Figure \ref{fig:planGrasp}.
In short, we define a series of approach radii $r_{a_i} \;  \forall i\, = 1.. numMoves$ that define concentric circles shrinking from the manipulator's starting tip pose towards the center of the object.
Given actuator limits, we then search for a series of feasible manipulator configurations $\boldsymbol{\kappa}_i^*$ that will place the robot's end-effector on these circles, parameterized by $r_a$ and $\phi$, while minimizing manipulator deformation.

\begin{figure}[htpb]
\centering
   \includegraphics[width=0.85\columnwidth, trim = 0mm 0mm 5mm 5mm, clip]{Figures/processing_control/grasp_object_planner.eps}
   \caption{Visualzation of the Grasp Object Planner. Concentric approach circles are shown in \emph{green} and are centered about the object shown in \emph{cyan}. The locally optimal approach configurations are shown in \emph{blue} and the gripper is shown in \emph{red}. The initially measured manipulator configuration is shown in black.}
   \label{fig:planGrasp}
\end{figure}

\begin{algorithm}[!htbp]
\begin{small}
  \SetAlgoLined\DontPrintSemicolon
  \KwIn{
  $\boldsymbol{\kappa}_{\textrm{meas}}$, $\mathbf{L}_{\textrm{meas}}$ $\gets$ measured arm configuration \;
  $\boldsymbol{\kappa}_{\textrm{off}}$ $\gets$ bias configuration offset at start \;
  $g_{\textrm{off}}$ $\gets$ gripper offset normal to end-effector\;
  $x_o$, $y_o$, $r_o$ $\gets$ object center coordinates and radius \;
  $N$ $\gets$ number of manipulator segments}
  \SetKwFunction{planGrasp}{planGrasp}
  \SetKwFunction{findOptimalConfig}{findOptimalConfig}
  \SetKwFunction{forwKin}{forwKin}
  \SetKwProg{myproc}{Procedure}{}{}
  \myproc{\planGrasp{}}{
  $\mathbf{w}_t \gets \forwKin \left( \boldsymbol{\kappa}_{\textrm{meas}}, \, \mathbf{L}_{\textrm{meas}}, \, N, \, L_N \right)$. \;
  $d_1 \gets \| \left[ x_o, \, y_o \right]^{\textrm{T}} \, - \, \mathbf{w}_t \|$. \;
  $d_2 \gets d_1 - r_o - g_{\textrm{off}}$. \;
  $numMoves \gets \lfloor \frac{d_2}{\Delta d} \rfloor$. \;
  $i$ = 0. \;
  \Repeat{$i$ = $numMoves$}{
    $i$ = $i \, + \, 1$ \;
    $r_{a_i} \gets d_1 \, - \, i\,\frac{d_2}{numMoves}$. \;
    $\boldsymbol{\kappa}_i^* \gets$ \findOptimalConfig{$r_{a_i}$}\;
  }
  \KwRet{$\boldsymbol{\kappa}_i^* \quad \forall i \, = 1.. numMoves$} \;}{}
  \setcounter{AlgoLine}{0}
  \SetKwProg{myproc}{Procedure}{}{}
  \myproc{\findOptimalConfig{$r_a$}}{
  $\begin{aligned}
    & \boldsymbol{\kappa}^* \, \gets \, \underset{\phi, \, \boldsymbol{\kappa}}{\text{min}}
    & & \mathbf{R} \, \left( \boldsymbol{\kappa} \, - \, \boldsymbol{\kappa}_{\textrm{off}} \right)^2. \\
    & \text{subject to}
    & &  \mathbf{w}_t \gets \begin{bmatrix} x_o \, + \, r \, \cos{\phi} \\ y_o \, + \, r \, \sin{\phi} \\ \phi \, + \, \frac{\pi}{2} \end{bmatrix}. \\
    & & & \mathbf{f} \gets \forwKin\left( \boldsymbol{\kappa}, \, \mathbf{L}, \, N, \, L_N \right). \\
    & & & \mathbf{w}_t - \mathbf{w}_{\textrm{off}}\left(r_o, \, \phi \right) - \mathbf{f} \, = \, \mathbf{0}. \\
    & & & \kappa_{n}^{\text{min}} \leq \kappa_n \leq \kappa_{n}^{\text{max}} \quad \forall \, n = 1 \, .. \,N. \\
    \end{aligned}$ \;
  \KwRet{$\boldsymbol{\kappa}^*$} \; }
  \setcounter{AlgoLine}{0}
  \SetKwProg{myproc}{Procedure}{}{}
  \myproc{\forwKin{$\boldsymbol{\kappa}$, $\mathbf{L}$, $i$, $s$ }}{
  \KwIn{$\boldsymbol{\kappa}$, $\mathbf{L}$, $i$ the segment of interest index, $s$ the arc length along the indexed segment}
  \eIf{$i = 0$}{
        $\theta_{i}(0) \gets \theta_0(0)$. \;
        $x_{i}(0) \gets 0$.\;
        $y_{i}(0) \gets 0$.\; }
    {
        $\left[ x_{i}(0), \, y_{i}(0), \, \theta_{i}(0) \right] \gets \forwKin \left(\boldsymbol{\kappa}, \, \mathbf{L}, \, i-1, \, L_{i-1} \right)$.\;
    }
    $\theta \gets \theta_{i}(0) + k_i s$. \;
    $x \gets x_{i}(0) + \frac{\sin{\theta}}{k_i} - \frac{\sin{\theta_{i}(0)}}{k_i}$. \;
    $y \gets y_{i}(0) - \frac{\cos{\theta}}{k_i} + \frac{\cos{\theta_{i}(0)}}{k_i}$. \;
  \KwRet{$\left[ x, \, y, \, \theta \right]^{\mathrm{T}}$ or $\left[ x, \, y \right]^{\mathrm{T}}$}}
  \caption{Grasp Object Planner}
  \label{alg:planGrasp}
\end{small}

@@

The procedure first determines the manipulator's current tip pose $\mathbf{w}_t$ and the Euclidean distance $d_1$ between the tip and the object's center. 
Next, considering the object's radius $r_o$ and the gripper normal offset $\mathbf{g}_{\textrm{off}}$, the minimal tip transit distance $d_2$ is calculated. 
$\mathbf{g}_{\textrm{off}}$ is the component of the end effector offset $\mathbf{w}_{\textrm{off}}$, which is normal to the end effector orientation. 
Also, the number of approach configurations $numMoves$ is determined as $\lfloor \frac{d_2}{\Delta d} \rfloor$, where $\Delta d$ is an allowable incremental distance. 
Using these parameters, approach radii $r_a$ are iteratively calculated and their corresponding locally optimal configurations are found using the \texttt{findOptimalConfig($r_a$)} procedure. 
This process is posed as a nonlinear optimization. 
Here, the objective function represents the summation of independently weighted manipulator curvatures and the constraints force the manipulator's tip to lie on and to be tangent to the approach circle. 
This process leverages the arm's forward kinematics \texttt{forwKin()} defined in \cite{marchese2014design} and reproduced in Algorithm \ref{alg:planGrasp} for convenience.

>>>>

\subsection{Existing Procedures}
The forward kinematics algorithm \texttt{forwKin()}, which we employ in this work, assumes piece-wise constant curvature according to \cite{webster2010design}. 
This algorithm was experimentally validated for the soft planar arm in \cite{marchese2014design}.
In order to uniquely fit a configuration representation to measured endpoint data in real-time, we use a previously developed single segment inverse kinematics algorithm \cite{marchese2014design} and refer to it in this work as \texttt{singSegInvKin()}.
The inputs to this block are the start and endpoint measurements in $\mathbb{R}^2$: $\mathbf{E}_n \; \forall n  = 1..N$, where $N$ is the number of segments composing the arm.
The outputs from this block are the representations of the measured manipulator configuration: $\boldsymbol{\kappa}_{\textrm{meas}}$ and $\mathbf{L}_{\textrm{meas}}$.
\rkk{Each segment of the manipulator is described by its measured curvature $\kappa_{\textrm{meas}}$ and its segment length $L_{\textrm{meas}}$}.
This work expands on the previously developed cascaded closed-loop curvature controller, whose input is target curvatures $\boldsymbol{\kappa}_{\textrm{target}}$ and whose output is the controlled adjustment of a fluidic drive cylinder array to resolve the error between $\boldsymbol{\kappa}_{\textrm{target}}$ and $\boldsymbol{\kappa}_{\textrm{meas}}$.
In this work we refer to it as the \texttt{curvatureController()}.

@@

\subsection{Autonomous Grasp-and-Place System}
\label{subsec:grasp-place-planner}
The robotic manipulation system is capable of autonomously performing grasp-and-place operations. 
A state flow diagram describing its sensing, planning and executions states is given in Fig. \ref{fig:grasp-and-place-planner}. 
A motion tracker constantly captures the position of the object and passes it along to a routine, which checks for the object to settle.
\rkk{We consider the object to have settled if it has not moved by more than a small $\epsilon$ for 2\unit{s}}.
After it has settled, the Grasp Object Planner receives the coordinates and radius of the settled object and together with the current curvature values of the arm and gripper, it solves a series of constrained nonlinear optimization problems to generate end-effector poses approaching the object.
Those end-effector poses are essentially waypoints for an optimized path the robot arm should take to get to the final position without the risk of pushing away the object before the gripper arrives there. 
Forcing the arm controller to follow those intermediate waypoints ensures that the arm moves to the object while its null space maintains a convex shape, bending away from the object. 
Furthermore, it allows the arm to move in smaller portions, decreasing the risk of large overshoots due to slip-stick friction between the roller supports and the ground.
This planner is described in more detail in Section~\ref{subsec:grasp_planner}.

@@

\subsection{Grasp Object Planner}
\label{subsec:grasp_planner}
A fundamental component of the grasp-and-place system is its ability to plan a feasible approach motion to the object.
That is, given the location $\left(x_o, \, y_o\right)$ and radius $r_o$ of a round object as well as the manipulator's current configuration $\boldsymbol{\kappa}_{\textrm{meas}}$ \rkk{and segment lengths $\mathbf{L}_{\textrm{meas}}$}, we determine a series of locally optimal manipulator configurations $\boldsymbol{\kappa}_i^* \; \forall i \, = 1.. numMoves$ that will, if sequentially achieved, bring the manipulator gradually closer to the object while any part of the arm is not touching the object.

We refer to these as approach configurations.
The process for determining these approach configurations is detailed in the \texttt{planGrasp()} procedure within the Grasp Object Planner, see Algorithm \ref{alg:planGrasp}.
The planner is visualized in Figure \ref{fig:planGrasp}.
In short, we define a series of approach radii $r_{a_i} \;  \forall i\, = 1.. numMoves$ that define concentric circles shrinking from the manipulator's starting tip pose towards the center of the object.
Given actuator limits, we then search for a series of feasible manipulator configurations $\boldsymbol{\kappa}_i^*$ that will place the robot's end-effector on these \rkk{green} circles, parameterized by $r_a$ and $\phi$, while minimizing manipulator deformation.

\begin{figure}[htpb]
\centering
   \includegraphics[width=0.85\columnwidth, trim = 0mm 0mm 5mm 5mm, clip]{Figures/processing_control/grasp_object_planner.eps}
   \caption{Visualization of the Grasp Object Planner. Concentric approach circles are shown in \emph{green} and are centered about the object shown in \emph{cyan}. The locally optimal approach configurations are shown in \emph{blue} and the gripper is shown in \emph{red}. The initially measured manipulator configuration is shown in black.}
   \label{fig:planGrasp}
\end{figure}

\begin{algorithm}[!htbp]
\begin{small}
  \SetAlgoLined\DontPrintSemicolon
  \KwIn{
  $\boldsymbol{\kappa}_{\textrm{meas}}$, $\mathbf{L}_{\textrm{meas}}$ $\gets$ measured arm configuration \;
  $\boldsymbol{\kappa}_{\textrm{off}}$ $\gets$ \rkk{measured manipulator} configuration at start \;
  $g_{\textrm{off}}$ $\gets$ gripper offset normal to end-effector\;
  $x_o$, $y_o$, $r_o$ $\gets$ object center coordinates and radius \;
  $N$ $\gets$ number of manipulator segments}
  \SetKwFunction{planGrasp}{planGrasp}
  \SetKwFunction{findOptimalConfig}{findOptimalConfig}
  \SetKwFunction{forwKin}{forwKin}
  \SetKwProg{myproc}{Procedure}{}{}
  \myproc{\planGrasp{}}{
  $\mathbf{w}_t \gets \forwKin \left( \boldsymbol{\kappa}_{\textrm{meas}}, \, \mathbf{L}_{\textrm{meas}}, \, N, \, L_N \right)$. \;
  $d_1 \gets \| \left[ x_o, \, y_o \right]^{\textrm{T}} \, - \, \mathbf{w}_t \|$. \;
  $d_2 \gets d_1 - r_o - g_{\textrm{off}}$. \;
  $numMoves \gets \lfloor \frac{d_2}{\Delta d} \rfloor$. \;
  $i$ = 0. \;
  \Repeat{$i$ = $numMoves$}{
    $i$ = $i \, + \, 1$ \;
    $r_{a_i} \gets d_1 \, - \, i\,\frac{d_2}{numMoves}$. \;
    $\boldsymbol{\kappa}_i^* \gets$ \findOptimalConfig{$r_{a_i}$}\;
  }
  \KwRet{$\boldsymbol{\kappa}_i^* \quad \forall i \, = 1.. numMoves$} \;}{}
  \setcounter{AlgoLine}{0}
  \SetKwProg{myproc}{Procedure}{}{}
  \myproc{\findOptimalConfig{$r_a$}}{
  $\begin{aligned}
    & \boldsymbol{\kappa}^* \, \gets \, \underset{\phi, \, \boldsymbol{\kappa}}{\text{min}}
    & & \mathbf{R} \, \left( \boldsymbol{\kappa} \, - \, \boldsymbol{\kappa}_{\textrm{off}} \right)^2. \\
    & \text{subject to}
    & &  \mathbf{w}_t \gets \begin{bmatrix} x_o \, + \, r \, \cos{\phi} \\ y_o \, + \, r \, \sin{\phi} \\ \phi \, + \, \frac{\pi}{2} \end{bmatrix}. \\
    & & & \mathbf{f} \gets \forwKin\left( \boldsymbol{\kappa}, \, \mathbf{L}, \, N, \, L_N \right). \\
    & & & \mathbf{w}_t - \mathbf{w}_{\textrm{off}}\left(r_o, \, \phi \right) - \mathbf{f} \, = \, \mathbf{0}. \\
    & & & \kappa_{n}^{\text{min}} \leq \kappa_n \leq \kappa_{n}^{\text{max}} \quad \forall \, n = 1 \, .. \,N. \\
    \end{aligned}$ \;
  \KwRet{$\boldsymbol{\kappa}^*$} \; }
  \setcounter{AlgoLine}{0}
  \SetKwProg{myproc}{Procedure}{}{}
  \myproc{\forwKin{$\boldsymbol{\kappa}$, $\mathbf{L}$, $i$, $s$ }}{
  \KwIn{$\boldsymbol{\kappa}$, $\mathbf{L}$, $i$ the segment of interest index, $s$ the arc length along the indexed segment}
  \eIf{$i = 0$}{
        $\theta_{i}(0) \gets \theta_0(0)$. \;
        $x_{i}(0) \gets 0$.\;
        $y_{i}(0) \gets 0$.\; }
    {
        $\left[ x_{i}(0), \, y_{i}(0), \, \theta_{i}(0) \right] \gets \forwKin \left(\boldsymbol{\kappa}, \, \mathbf{L}, \, i-1, \, L_{i-1} \right)$.\;
    }
    $\theta \gets \theta_{i}(0) + k_i s$. \;
    $x \gets x_{i}(0) + \frac{\sin{\theta}}{k_i} - \frac{\sin{\theta_{i}(0)}}{k_i}$. \;
    $y \gets y_{i}(0) - \frac{\cos{\theta}}{k_i} + \frac{\cos{\theta_{i}(0)}}{k_i}$. \;
  \KwRet{$\left[ x, \, y, \, \theta \right]^{\mathrm{T}}$ or $\left[ x, \, y \right]^{\mathrm{T}}$}}
  \caption{Grasp Object Planner}
  \label{alg:planGrasp}
\end{small}

@@

The procedure first determines the manipulator's current tip pose $\mathbf{w}_t$ and the Euclidean distance $d_1$ between the tip and the object's center. 
\rkk{The arc length input to the arm's forward kinematics is the $N$-th element of the segment lengths $\mathbf{L}_{\textrm{meas}}$.}
Next, considering the object's radius $r_o$ and the gripper normal offset $\mathbf{g}_{\textrm{off}}$, the minimal tip transit distance $d_2$ is calculated. 
\rkk{The end effector offset $\mathbf{w}_{\textrm{off}}$ describes the distance from the root of the gripper, to an offset point close to the lower end of the gripper's palm. It is visualized in the top left corner of Fig.~\ref{fig:grasp-and-place-planner}.}
\rkk{The length} $\mathbf{g}_{\textrm{off}}$ represents the component of the end effector offset $\mathbf{w}_{\textrm{off}}$, which is normal to the end effector orientation. 
Also, the number of approach configurations $numMoves$ is determined as $\lfloor \frac{d_2}{\Delta d} \rfloor$, where $\Delta d$ is an allowable incremental distance. 
Using these parameters, approach radii $r_a$ are iteratively calculated and their corresponding locally optimal configurations are found using the \texttt{findOptimalConfig($r_a$)} procedure. 
This process is posed as a nonlinear optimization. 
Here, the objective function represents the summation of independently weighted manipulator curvatures and the constraints force the manipulator's tip to lie on and to be tangent to the approach circle. 
This process leverages the arm's forward kinematics \texttt{forwKin()} defined in \cite{marchese2014design} and reproduced in Algorithm \ref{alg:planGrasp} for convenience.
